\documentclass[a4paper,10pt]{article}
\usepackage[left=0.6in, right=0.6in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Color and link setup
\definecolor{darkblue}{RGB}{0,0,139}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
}

% Section formatting - customized for the "larger first letter" design
\titleformat{\section}{\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1.5ex}{1ex}

\begin{document}

\pagestyle{empty} % Remove page numbers

% Header 
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\begin{tabular}{l}
    {\Huge \textbf{Deepak}} \\
    \textit{Software Engineer}
\end{tabular}
&
\begin{tabular}{r}
    \textbf{Mobile:} +91-7987600067 \\
    \textbf{Email:} \href{mailto:deepakmardi22@gmail.com}{deepakmardi22@gmail.com} \\
    % \textbf{Portfolio:} \href{https://www.iamdeepakmardi.xyz/}{website}
\end{tabular}
\end{tabular*}

% Summary
\section*{\normalfont {\LARGE S}\large UMMARY}
Full Stack Software Engineer with 1.5+ years experience building scalable backend systems and high-performance web applications. Focused on AI-assisted workflows to accelerate delivery, automate tasks, and improve reliability. Strong problem-solving, quick learner, and collaborative team player optimized for agile environments.

% Education
\section*{\normalfont {\LARGE E}\large DUCATION}
\noindent
\textbf{IIT Kharagpur} \hfill \textit{May 2022} \\
Dual Degree in Metallurgical and Materials Engineering \\[4pt]
\textbf{Krishna Public School (CBSE)} \hfill \textit{2016} \\
12th Standard - 69\%

% Experience
\section*{\normalfont {\LARGE E}\large XPERIENCE}

\noindent
\textbf{Epek Software Solutions} | \textit{Software Engineer} \hfill \textit{Oct 2025 – Jan 2026}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Stabilized API performance and redesigned aggregation pipelines using TypeScript, JavaScript, and MongoDB.
    \item Decreased peak server load by building an asynchronous Node.js webhook pipeline for queue batching.
    \item Improved transactional email reliability by integrating SendGrid and event webhooks with automated retries.
    \item Refactored monolithic UI into a modular architecture using React to establish shared state management.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Arcs Design Studio} | \textit{Co-Founder} \hfill \textit{Jan 2025 – Oct 2025}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Developed front-end architecture for multiple production SaaS products using Next.js and TypeScript.
    \item Architected backend web services using Node.js and PostgreSQL to manage concurrent data.
    \item Managed project scoping and delivery timelines by translating technical requirements for stakeholders.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Epek Software Solutions} | \textit{Software Engineer} \hfill \textit{May 2024 – Jan 2025}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Enabled high-frequency radius searches by creating a centralized spatial API using React.js and Docker.
    \item Standardized multi-client contracts through structured validation and error-handling middleware.
    \item Streamlined geospatial search queries under load by tuning 2dsphere indexes in DigitalOcean.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Tablt Pharmacy} | \textit{Product Development Intern} \hfill \textit{Apr 2021 – Aug 2021}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Developed a chatbot integrating Tiledesk and Dialogflow using JavaScript, HTML, and CSS.
    \item Enhanced automated responses and trained ML-based FAQ intents in collaboration with developers.
\end{itemize}

% Projects
\section*{\normalfont {\LARGE P}\large ROJECTS (PROOF OF WORK)}

\noindent
\textbf{Snapterra} - Full Stack \href{https://github.com/iamdeepakmardi/snapterra}{(GitHub)} \hfill \textit{}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Built a media management system with JWT authentication, secure uploads, and fast media handling.
    \item Designed a normalized many-to-many tagging system with fast search and preview for asset organization.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{Tabula} - Full Stack \href{https://tabula-n2dv.vercel.app}{(Live Demo)} \hfill \textit{}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Built a real-time collaborative whiteboard with concurrent editing and persistent state sync using Convex.
    \item Implemented role-based access control and integrated Excalidraw and EditorJS in Next.js.
\end{itemize}

\vspace{4pt}
\noindent
\textbf{My Kata Machine} - Developer Tool \href{https://github.com/iamdeepakmardi/my-kata-machine}{(GitHub)} \hfill \textit{}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt]
    \item Built a configurable code generation system to scaffold DSA problems with predefined types and tests.
\end{itemize}

% Skills
\section*{\normalfont {\LARGE S}\large KILLS}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt]
    \item \textbf{Languages:} JavaScript, TypeScript, Python, Shell/Bash.
    \item \textbf{Frontend \& Backend:} React, Node.js, Express, REST APIs, Tailwind, Redux.
    \item \textbf{Databases \& DevOps:} MongoDB, PostgreSQL, Docker, Git, CI/CD, System Design, Linux.
    \item \textbf{AI Workflows:} Github Copilot, Claude Code, Cursor.
\end{itemize}

\end{document}
